Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-11-18 refreport/response.tex

We further note that splitting the paper up into two separate pieces
provides structural challenges, and will serve to increase the total
page count.  Structurally, Section 2 (the ``overview'' section) would
need to be split into two pieces, and the component that discusses the
microphysics will be somewhat confusing on its own, as these modules
act as sink and source terms for the fluid equations that would in
principle be described in a separate paper.  It's not clear where
Section 10 (``Analysis''), Section 12 (``Parallel strategy and
performance''), and Section 13 (``Code development methodology'')
would logically go -- some of these sections apply to all physics
packages in the code (e.g., Section 12), and others to none in
particular (e.g., Section 13).  Similarly, Section 11.1 (``Verifying
and validating the Enzo code'') describes the \enzo\ test suite, which
is used for all aspects of code testing (including both the
fluid/gravity/AMR algorithms \textit{and} the microphysics), and also
for code comparisons that test many different aspects of the code,
often in combination.  In order for these sections to make sense, and
to address test problems that are split between two papers, several of
these sections would need to be either duplicated or require an
extensive amount of cross-referencing between papers Furthermore,
separate introductions, discussions, and conclusions will by necessity
be mutually referential and, in some sense, duplicates of each other.
Together, this will not serve to either decrease page count or
increase clarity for the reader.

\section{Additional changes}

In addition to directly addressing concerns expressed by the referee,
we have fixed additional typos in the paper.  These include:

\begin{enumerate}
\item  We have corrected a typo in the equation describing the Jeans
  length refinement criterion (Section 3.6, Equation 29).

\item We have updated our description of the shear refinement
  criterion (Section 3.6, Equation 30).

### 2013-11-18 code-tests.tex
Removed commented-out text from lots of files - basically vestigial junk.
Adding ionization balance test.
adding brio & wu mhd test
Point out that we also test the code in the other enzo method papers (MHD, radiation).

The \enzo\ test suite (described in Section~\ref{sec.tests.suite})
contains hundreds of test problems that probe the code's behavior in a
wide range of physical circumstances, and explicitly tests each physics
package in the \enzo\ code, both individually and in combination.  It
is impractical to include a substantial fraction of these problems in
a method paper; as a result, we have chosen to publish the results of
only a small subset of particularly crucial test problems here.  If
the interested reader desires, they can download \enzo\ and
\texttt{yt}, run the test suite, and see the results of any other test
problem and its comparison to an analytic solution (if available), or
to a ``gold standard'' solution from a stable version of \enzo.

@@

% General structure for each test problem: Outline how the test problem
% is constructed (initial and boundary conditions), the analytical
% solution, why we have in the paper (what does it break, or what flaw
% does it expose (not in enzo of course)), a plot showing how well enzo
% solves said test problem, and a brief description of the plot and how
% awesome enzo is.

@@

@@

>>>>

The \enzo\ test suite (described in Section~\ref{sec.tests.suite})
contains hundreds of test problems that probe the code's behavior in a
wide range of physical circumstances, and explicitly tests each physics
package in the \enzo\ code, both individually and in combination.  It
is impractical to include a substantial fraction of these problems in
a method paper; as a result, we have chosen to publish the results of
only a small subset of particularly crucial test problems here.  If
the interested reader desires, they can download \enzo\ and
\texttt{yt}, run the test suite, and see the results of any other test
problem and its comparison to an analytic solution (if available), or
to a ``gold standard'' solution from a stable version of \enzo.
We also note that there are many other \enzo\ test problems in the
associated papers which describe individual methods, including:
MHD-CT \citep{Collins10}, MHD-Dedner \citep{WangAbelZhang08,
WangAbel09}, Radiation-FLD \citep{NBHBROW2007,
ReynoldsHayesPaschosNorman2009, NRS2009}, Radiaton-ray-tracing
\citep{Wise11_Moray}.

@@

@@

\input{tests-bw}

@@

\input{tests-ionbalance}
